\chapter{Magic}\label{chapter-magic}

\section{Properties}\label{mp}
This section provides
magical properties for alchemists and
Game Masters to imbue normal items with.
These properties are described in general terms,
but the Game Master should be more descriptive and specific
to make the item more unique, special, or interesting.
These properties can be imbued into any item from a ring to a sword.
The requirements to activate the properties, therefore, should be
described by the Game Master.
Consider, for instance, the difference between a ring and sword.
The character would get the benefits from wearing the ring or unsheathing the sword,
but the moment that the ring is removed or the sword sheathed, then the benefits are
immediately lost.

The value of these properties varies from alchemist to alchemist.
The Game Master should set the values as necessary to maintain game balance but also
allow the characters to legitimately buy magical items.
Of couse, the characters are not entitled and the alchemist's shop may or may not have
the item in inventory or be staffed by anyone who could create the item for the characters.
This can be a random determination made by the Game Master or simply a decision made at the
Game Master's discretion.

Properties can stack on a single item but this solely at the Game Master's discretion.
Some of these properties are similar to those found in the rule book.
Where there is conflict there is no conflict;
these are simply different magical properties which can be imbued into items.
Some of these properties can only be imbued into weapons and some properties
differ according to the type of item imbued.
The descriptions point these instances out and describe them.

Note that the items imbued with these
magical properties may have more creative
names given to them by the alchemist or/and
popular culture.

\begin{description}
\item[Agility.] This property imbues the item with a Physical Prowess attribute bonus of +2.

\item[Amplified damage.]
This magical
property imbues
weapons with a chance of doing double damage to the target struck.
When damage is done there is a 10\% chance of dealing double damage.
This means doubling the damage rolled on the normal damage dice, not rolling twice the
normal amount of damage dice.

\item[Animated.]
This property imbues the object with its own
motion to follow the owner around.
When a shield is imbued with this magical
property, then the shield will also work to
defend the owning character.
When attacked the defender has two chances
to defend the attack. The first is the
animated shield which gains the character's
parry bonus.
When a weapon is imbued with this magical
property,
then the weapon will also attack the
owning character's opponents.
The weapon has 4 attacks per melee and it 
enjoys the owning character's bonus to
strike with using that weapon.
Other objects imbued with this magical
property will follow the owning character
around.
If the imbued object is itself a magical
item, the object retains all of its other
properties.

\item[Anti-magic.] The item imbued with this
magical property gives the owning character
the power to expend his or her own P.P.E.\ in
which can cancel out the effects of cast magic
if the P.P.E.\ expended is greater than that which was
expended by the caster to cast the invocation.
This is a guessing, of course, and the Game
Master will alert the
character of the results.

\item[Anti-regeneration.]
This property is specifically for weapons.
It imbues the weapon with magic that disrupts living beings' natural abilities to
regenerate damage.
When the weapon successfully deals damage to the being's body,
then a saving throw against magic must be made with a --5 penalty.
If the saving throw is successful then the being regenerates at
half the efficiency for 3D4 hours.
If the saving throw is failed then the being does not regenerate whatsoever
for 3D4 hours.

\item[Anti-seduction.]
The owner of this magical item becomes
less suseptible to seduction attempts
by others against the character.
The character attempting to seduce
the owner of this item does so with
penalty of -30\%.
The character is further immune to
the effects of exceptional
Mental Affinity and Physical Beauty
attributes.

\item[Archery.]
Any item imbued with this magical
property grants the owner improved
archery skills.
The owner must already be an archer.
The bonuses are +2 Rate of Fire and to
Strike.

\item[Arrow stopper.]
This magical property is often imbued on
shields and armours, but in reality it could
any object may be imbued with the magical
property.
The object can be activated and deactivated
by the owner of the object.
When it is deactivated the object does not
register magical whatosever.
It also does not have the \emph{arrow stopper}
magical property.
Whatever object is imbued with this magical
property will have some kind of arrow design.

\item[Attribute booster.]
This property imbues the item with a +2 bonus to all of the character's attribute
numbers.
If attribute numbers are high enough to receive bonuses, then the character
receives those bonuses.
Once the item is dispossed, the bonuses to the attribute numbers---and
resulting exceptional bonuses---disappear immediately.

\item[Battery.]
For games using Potential Psychic Energy and magic,
this property imbues the item with the power to store P.P.E.
The item can store up to the same amount of P.P.E.\ as the character in possession of the
item.
The charge is taken from the character's P.P.E.\ reserves, however, which means the
character is temporarily at zero.
This is particularly powerful when combined with the \emph{wizardly power}
(see page~\pageref{mp:wizardly})
property.

\item[Caster.]
Possession of any object imbued with this
magical prpoperty reduces the P.P.E.\ needed
for invocations from first to seventh level
by half.
Also all invocations can be cast in just
one round of experience.
There is an additional bonus of
+1 Spell Strength for owners between
first and third level of experience
while characters fourth level or greater
enjoy +2 Spell Strength bonus.

\item[Cold protection.] This property imbues the item with cold resistance.
The character takes only half damage from all types of cold, including magical.
The character is never at risk of hypothermia and can operate in cold temperatures without
suffering penalties to skills requiring fine motor skills.

\item[Damage to P.P.E.] This property imbues the item with a special damage reduction
mechanism.
Upon taking damage to the body the possessor of
the item takes damage first to P.P.E.\ reserves.

\item[Critical strike.]
The weapon scores a critical strike when the wielder
rolls a natural 17, 18, 19, or 20.

\item[Darkness.] This property imbues the item with a light absorbing property,
which causes darkness in a three meter radius centered upon the possessor of the
item. Living beings caught in the darkness are essentially blind unless they have
nightvision as a natural ability or through an enchantment or psychic power.

\item[Defence.] This property imbues the item with properties according to type.
If the item is a piece of armour then the armour rating gets a +2 bonus and a 20\%
bonus to S.D.C.
If the item is anything else then the character gains +2 bonus to all defence rolls
in combat---these rolls that receive the defence bonus
are: dodge, parry, and roll with impact.

\item[Demon bane.] This property imbues the item with special properties according
to the type of item being imbued.
Weapons will deal an extra 2D6 damage to demons and devils and hold them at bay if
held high over the head for all to see.
Armours will gain a bonus of +2 to armour rating when being attacked by demons and devils
creatures.
All other items will grant the possessor a bonus of +2 to save against all magics
directed at the possessor
by demons and devils.

\item[Echolocation.]
This magical property imbues an item with the
physical phenomenon of echolocation.
This allows the possessor of the item to find
his or her way around in any non-vacuum.
This gives a character a +5\% bonus to Prowl
and +1 to Perception Rolls when using echolocation.

\item[Faerie bane.]
The owning character is +4 against faerie
magic.
If the faerie fails a Saving Throw against
magic, that means the creature will not be
able to cast any magical spells for 6D4 hours.

\item[Fire damage.] This property imbues the weapon with a bonus of 1D6 fire damage,
but only when doing damage to the target's body---as opposed to the target's armour;
half if the victim saves against magic.

\item[Firefighting.]
Items imbued with this magical
property allows the character to
extinguish natural and magical
fire.
The control over natural fire is
simple, automatic, and free.
But in order to control magical
the character needs to expend
P.P.E\ points---the character
must spend as many points as
the points spent to create the
magical fire.

\item[Fire protection.] This property imbues the item with fire resistance.
The character takes only half damage from all types of fire, including magical fires.

\item[Fleet feet.] This property imbues the item with a bonus of +20 to the character's
Speed attribute number.
When the item is dispossessed the bonus disappears immediately.

\item[Flying.] Common items imbued
with this magical property include
bicycles, brooms, and carpets.
The possessor of this magical item
is able to fly on the object which works
precisely like
\emph{fly as the eagle} spell at
fifth level proficiency.

\item[Fortune.] The possessor of this magical item is bestowed with either
$+1/+5\%$ \emph{or} $+2/+10\%$ on all D20 and percentage rolls.

\item[Glowing] This property imbues the item with natural sunlight.
This will keep vampires and other light phobic creatures and monsters
at bay, however, it cannot damage them or destroy them.
It is good for lighting a small room and the light can be activated and deactivated
on command---usually a verbal command which the alchemist reveals to the item's buyer
at the point of sale.

\item[Guardian.] The character cannot be
attacked by surprise or from behind;
sneak attacks are impossible against the
character; and, finally, the character does
not suffer from critical damage.

\item[Heat.]
The magic item generates heat
which radiates much like a small
fire.
The item imbued with this magical property
may or may not radiate light at the same
time it radiates heat from the object's
surface.
In any case the object will not cause any
damage when touched by bare flesh.

\item[Health.]
The ower of any item imbued with this
magical property enjoys improved
health.
The health benefits are in effect
only when the character is in direct
possession of the item.
The character gets +10 bonus to all
disease and poison related Saving
Throws---this includes toxins and
dangerous gases,
both lethal and nonlethal.
The character receives +10 Hit Points
and +20 S.D.C.
The character gains
+10\% to Save against coma/death.
The character also receives +5 to
P.E.\ attribute which could produce
further bonuses to coma/death.

\item[Horsemanship.]
The character gains the \emph
{Horsemanship: general} skill at
third level of experience.
If the character already has a
horsemanship skill,
the character gains +15\% to the
skill as well as +3 to all D20 rolls
related to the skill.

\item[Jumping.]
This magical property improves the
owner's natural jumping ability.
The character owing the imbued
item can jump like this.

\item[Learning.]\label{mp:learning}
This property imbues the item with the power of granting the character a 5\% bonus to
all experience points earned from academic and other non-violent activities.
Compare this property with \emph{warrior's spirit} on page~\pageref{mp:warriorspirit}.

\item[Life.]
This property imbues the item with life nourishing properties.
The property imparts on the imbued item
a bonus of twenty Hit Points and
a doubled healing rate.
When the item is dispossessed, then the bonus Hit Points
disappear as well
If the character 
has twenty or less Hit Points,
then the character is immediately reduced to just one Hit Point.

\item[Life leech.]
This property may only be imbued into weapons.
When dealing damage to the body of a living being,
the weapon's wielder is healed by half the amount of
damage done by the successful strike.

\item[Lower resistance.]
When an object is imbued with this magical
property, then everyone within 10 feet
(3 m) except for the owner of the object
has all resistances removed.
The victim gets a chance at a Saving
Throw against magic at -2 to avoid the
effects of the property.
The owner may with a thought remove the
effects from friendly characters.
The maximum is 1D4 +4 characters; anyone
else must Save against magic and gains a
+2 bonus for being friendly.

\item[Magic resistance.]
This property imbues the item with resistance to magical damage and influences.
This magical property reduces the amount of damage taken from spells by half and
imparts a +2 bonus to save against all types of magic.

\item[Mineral detection.] The item
imbued with this magical property alerts
the owner to the presence of minerals
nearby.
The magic property can detect up to
4D4 individual minerals.
The number of detectable minerals
determine the cost of the item.

\item[Natural armour.]
While in possession of any item
imbued with this magical property,
the owner gains a Natural Armour
Rating of 14;
if the owning character already has
a Natural Armour Rating, then the
owner gains an additional +2 to the
Natural Armour Rating.

\item[Neutralise poison/toxin.]
This magical property works like
level five \emph{Negate Poison}
invocation but it only costs two P.P.E.\ to activate.

\item[Perception.]
The character owning an item imbued
with this magical property receives a
bonus to Perception.
Thus, the character is +3 to all
Perception Rolls.

\item[Poison damage.] This property imbues the weapon with a bonus of 2D6 poison damage,
but only when doing damage to the target's body---as opposed to the target's armour;
half if the victim saves against lethal posion.

\item[Poison resitance.] This property imbues the item with a bonus of +2 to save against
all types of poisons and toxins and gases.

\item[Quick strike.]
Only weapons may be imbued with
this magical property.
If the weapon strikes and deals any damage whatsoever,
then the victim loses the option to defend against the attack
in any way except to attempt to dodge it.
The reason for this is the swiftness of the attack,
magically enhanced,
is too quick for the defender.
This can be used twice per opponent per melee round.
The power is use it or lose it power.

\item[Seduction.] The character who
owns any item imbued with this magical
property becauses exceptionally
seductive.
The character seduces at 85\%
proficiency.
If the character already has this skill
it bumps up to 85\% if the profiency is
less than 85\%.

\item[Shopping.] This property imbues a luck charm or other item such that
the character always gets a 20\% discount when shopping for standard, non-magical items
and equipment; this may or may not, according to the Game Master's discretion or random
determination, include armour and weapons.

\item[Skills bonus.] This property can give a bonus to a specific skill,
a category of skills, or to all skills known by the character.
The bonus is +10\% and may be adjusted by the Game Master according to the
circumstances.

\item[Sonic resistance.]
The owner of the object with this magical
property gains resistance to all sonic
attacks---both physical, psychical, and
magical.

\item[Speed weapon.] This property imbues
weapons with four extra attacks per melee round.
The character can only
use the extra attacks with the imbued weapon.

\item[Stealth.] This magical property
imbues the item with the power to
improve the owning character's
phyiscal prowess.
The character gains a
+5 bonus to the P.P.\ attribute.
The owner also gains +20\% Prowl
skill.
If the owner does not have the Prowl
skill, then the character Prowls at
50\% proficiency.

\item[Sustenance.]
The owner of the item imbued with this
magical property do not need to eat.
The need for food and rest is greatly
diminished. The character needs to
only eat once a week and sleep only
works just like the Guardian needing
sunlight.

\item[Swift missile.]
This property can only be imbued into missile weapons
and it allows the weapon's wielder to fire the weapon
at twice the character's
normal rate of fire or 6 shots per melee
round, whichever is greatest.

\item[Undead bane.] This property imbues the item with special properties according
to the type of item being imbued.
Weapons will deal an extra 2D6 damage to undead creatures and hold them at bay if
held high over the head for all to see.
Armours will gain a bonus of +2 to armour rating when being attacked by undead
creatures.
All other items will repel the undead from the possessor;
the possessor can effectively turn away a number of undead creatures equal to
the character's level of experience.

\item[Undead attractor.]
Undead within a 100 foot radius is attracted
to the character who owns the object.
The undead creatures will not pay attention
to any living being except for the owner of
the object.
This also includes necromancers and anyone
else capable of influencing or directing the
undead.
The undead become ``obssessed'' with
the owner of the magical item.

\item[Warrior's spirit.]\label{mp:warriorspirit}
This property imbues the item with the power of granting the character a 5\% bonus
to all experience points earned in combat.
Compare this property with the \emph{learning} property on page~\pageref{mp:learning}.

\item[Wizardly power.]\label{mp:wizardly}
When worn by a magic user the mage can cast twice the normal number
of spells per day or doubles the amount of P.P.E.\ available for
spellcasting.
\end{description}

\section{Relics and artifacts}
The items described in this section are unique items.
They are legendary and it is entirley possible that they are the stuff of myth
and do not exist at all.
They at times use the magical properties described in Section~\ref{mp} starting on
page~\pageref{mp}, however, they also use modified versions of the properties or even
have properties that are unique to the item.
The Game Master is of course free to use these properties in other magical items.

Section~\vref{sec:legendary-paladins} describes some the legendary paladins of
the Something who possessed these items.
However,
not all of these items were possessed by these paladins.
Some where in the possession of great magic users
(see Section~\vref{sec:legendary-mages} for about these individuals).
\begin{description}

\item[Al's fork.]
A magical item in the form of a musician's tuning
fork.
For to use the item, the character simply taps the
fork against a lock and the tuning fork guides the
character's hand and lock picks to pick the lock.
The character gains a +25\% bonus to pick the lock.
If the character fails, the character can try again
but only with a +10\% bonus.
If the character fails a second time,
the fork may not be used on the same lock for another
year.

\item[Alkbam's crown.]
This magical crown endows the character with a bonus
of fifty extra Hit Points and a bonus of +2 to Physical Strength
and Physical Endurance attribute numbers.
Finally,
the crown gives the character the ability to Turn Dead 4x daily.
\item[Alkbam's leather gloves of skill.]
These magical leather gloves give the character a
bonus of 20\% to \emph{all} skills.
\item[Alkbam's undead slayer.]
This is a one-handed long sword that provides the wielder
with the following bonuses when fighting against undead
creatures and monsters:
+2 to initiative,
+2 attacks per melee, --2 to the character's opponent's
D20 combat rolls, double damage,
and Healing Touch 4x daily.
\item[Anselm's tower.]
This large metal shield is indestructible and provides a bonus of +2 to parry.
Whenever the wielder successfully parries with the
shield the difference between the attacker's strike
roll and the defender's parry roll is healed by the
wielder of the shield.
For instance, if the attacker rolls a ten and the
defender rolls---with bonuses---a
fifteen, then the defeneder is healed five points of damage automatically.
\item[Anselm's vigour.]
This two-handed sword heals the wielder half of the
slain foe's maximum Hit Points when slain by the
weapon.
\item[Baangor's ring of protection.]
This ring magically absorbs damage taken when worn.
The amount of damage changes with each melee round.
To determine how much damage is absorbed the wearer's
rolled initiative is added to one hundred and the sum
is divided by four, roudning up.
So if the player has an initiative roll of 20, then
the ring will absorb as a percentage:\[
\frac{100 + 20}{4} = 30\%
\]

\item[Begga's climbing gloves.]
This magical pair of leather gloves
provide the character with the ability
to climb at 90\% proficiency.
The gloves have an added bonus of +30\%
to the character's swimming skill---if 
the
character does have the swimming skill,
then there is no effect.

\item[Begga's pearl.]
This is a small pearl which,
when put in the mouth,
removes the character's
requirement for oxygen.
This means the charcter can be underwater,
in space, or anywhere there is noxious fumes.
Because the character not required to breathe,
this magical item can be used to simulate death---within
reason.

\item[Fick's mageblade.]
The wizard gains a bonus of +2 to spell strength and can
cast four extra spells per day (or +20\% extra P.P.E.).
The dagger can also be used to illuminate small rooms
like a lantern,
however, this magical light has no affect on vampires
and other such creatures.

\item[Fick's trekking boots.]
When worn, the character does not fatigue from walking.
This means the character can march indefinitely,
however, it only applies to walking and not running.

\item[JaQo's crystal ball.]
This magical crystal ball can be activated with
just five P.P.E.\ points.
The activation of the crystal ball gives the
character access to fifth level of experience
equivalent of some temporal magic spells yet to
be determined.
The cystal ball is always capable of detecting
magic and evil.

\item[JaQo's mirror.] This large magical mirror
can be activated by a character spending twenty-five
P.P.E.\ points.
The mirror operates at the equivalent of an eigth
level invocation of one of the following:
clairvoyance, remote viewing, or calling.
The Game Master can determine randomly the affect
by rolling on the following table:
\begin{table}[ht]
\centering
\begin{tabular}{rl}
\toprule
{\bfseries Roll} & {\bfseries Results} \\ 
01-33&Clairvoyance \\ 
34-66&Remote viewing \\ 
66-99&Calling \\ 
00&Roll again \\
\bottomrule
\end{tabular}
\caption{Random effects of JaQo's mirror.}
\label{table-jaqo-mirror}
\end{table}

\item[JaQo's spy glass.]
This is a single lens which can be put in any frame
or pince-nez or simply hold up to one's eye.
When looking through the lens,
the seer is able to see the invisible,
to see characters magically concealed---such
as with Shadow Meld.
Also the character gains +15 to save against
the Multiple Image magical invocation.

\item[Limm's holy beads.]
This is a string with a number of beads evenly
space along its length.
The pattern is four smaller beads then one larger
bead; this pattern is repeated four times.
The result here twenty small beads and five large
beads.
The smaller beads are pinched between the fingers and
a simple, minor prayer is uttered while the other hand
is placed on the patient.
After a minute the patient is restored half of his or
her Hit Points and S.D.C.
The larger beads will will heal one hundred percent.
Each smaller bead may only be used once a week while
each larger bead may only be used once a month.

\item[Limm's holy symbol.] When held in the hand of
priest of light, the priest casts magic spells at
four levels of experience higher than the priest's
actual level of experience.
Additionally, the priest casts all magical spells
with +2 Spell Strength.

\item[Limm's robe.]
This is a simple monk's robe.
When wearing the robe, the character fights
and defends himself or herself in hand to hand
unarmed combat as if tenth level of experience.
If the character is tenth level or experience 
or higher, there is no effect.

\item[Limms' vest.] This vestment improves the
the priest of light's abilities, magic, and powers.
We need to give some more of a description here.

\item[Mbo's might.]
This battle axe reduces an opponent's armour rating by
two for 1D4 melee rounds.
They stack.
Critical strikes reduce it by one for a total of three.
When the duration ends,
the armour rating returns to normal.
This will affect natural armour rating on creatures.
This gives all attackers a better chance to striking.

\item[Nimble's boots of kicking.]
These hard leather boots are made for kicking.
The wearer of these boots gains a bonus of +2 to strike
and +6 to damage when
kicking.

\item[Sabina's inspiration.]
A bracelet that adds a bonus of +2/+10\% to all
rolls requiring a D20 or percentile.
It also provides +1D6 damage.

\item[Sabina's interpretter.]
This item is a necklace that permits the wearer to speak
any language of the Palladium World,
but the user cannot read or write the languages.
It is possible to understand basic communication as on
a children's level;
the level is at level one.
Note also that when the user of this magical item speaks
everyone around hears the words in their preferred language.
That means if the user is speaking to a human from the east
and an elf, then the human will hear it in eastern while the
elf will hear it in elven.

\item[Sabina's reflection.]
This suit of studded leather armor causes the
attacker to sustain the same amount of damage
done to the armour to his or her own armour.
If the attacker is not wearing armour then the damage
is done to the body.
Attacks that defeat the armour rating do not
reflect fatigue.
Per strike there is a 10\% chance to reflect back 100\% of damage
and a 20\% chance for 50\% damage to be reflected.

\item[Sabina's sallet.]
This helmet gives the wearer elemental resistance.
Elemental damage is cut in half if it is magical damage
otherwise the wearer takes no damage at all from
elemental attacks.
The wearer also gains 1.5 times bonus to Hit Points and
a bonus of +2 to Physical Endurance attribute.

\item[Sabina's torch.]
This magical mace has a 10\% chance of casting
Mirror Image equivalent to a level five magic user.
There is a further 5\% chance of casting the same
for each strike in succession.
The weapon also gives the wielder a bonus of +20\%
to Prowl skill and inflicts 6D6+6 damage to undead
monsters and solar phobic creatures like vampires.

\item[Suo's dust.] Suo is an assassin of legend.
This small sack of magical dust is used for
countertracking.
When the dust hits the ground it disappears and
anyone trying to track the character by any
means---sight, sound, smell, magic---does so with
a penalty of -45\%.

\item[Suo's rope.] This magical rope belonged to the
legendary assassin Suo.
The item has several magical properties.
The rope can be used with a grappling hook.
If there is an anchor point to be found,
the grappling hook will find it and stick to it.
The hook can just as easily be recalled.
Characters with grappling hook weapon proficiency
receive a +2 bonus when using this magical length
of rope.
The rope will self coil and never gets in
unintended knots.
This also means that the rope gives the character
the Rope WOrks skill at 85\% proficiency.
If the character already has the skill, the player's
choice is to apply a bonus of +10\% to the skill.
The rope is 150 feet (45 m).

\item[Sword of the Elements.]
This legendary claymore sword provides the wielder with
a
bonus of +2 to Physical Strength and Prowess attributes.
It also allows the wielder to cast each of the following
spells four times daily: \ldots{}.

\item[Tabar's resistance.]
This suit of magical chain mail has +3 armour rating and
double the usual S.D.C.\ for chain mail armour.
The armour takes half damage from magic elemental attacks
and no damage from normal elemental attacks.

\item[Tabar's wonder.]
This spear produces a random effect upon any successful
strike.
There is a
50\% chance that a random effect will be fired.
Note that the effect still fires whether or not
the defender successfully defends;
however, some of the effects are nullified by
successful defences.
The random effects are provided in Table~\ref{table-tabarwonder}.
\begin{table}[ht]
\centering
\begin{tabular}{rl}
\toprule
{\bfseries Roll} & {\bfseries Results} \\ 
01-10&Critical strike \\ 
11-20&Chain of lightning \\ 
21-30&Antiregeneration \\ 
31-40&Blinding Flash (level 5) \\ 
41-50&Steal attack \\ 
51-60&Defender is --2 \\ 
61-70&Defender loses initiative \\ 
71-80&Knockdown \\ 
81-90&Free second attack \\ 
91-00&Quick strike \\ 
\bottomrule
\end{tabular}
\caption{Random effects of Tabar's wondrous spear.}
\label{table-tabarwonder}
\end{table}

\item[Talon's spellbook.]
Nothing is known about Talon.
The name is only known about due to the existance
of this magical tome.
The book is filled with twenty pages.
One each page a spell is described.
The character who owns the spellbook can read
each page as a scroll up to three times daily.
If the owner of the tome is a man of magic,
then the character can learn the spells.
If the character spends three hours, the character
can cast the spell once.
If the character spends three months studying the
spell with intensity, then the character has learned
how to cast the spell without having to study the
tome.
The pages are written in silver and cannot be
destroyed or reproduced.
If anyone makes a cioy, the runes and
words fade or alter shape
such that they are meanginless.
It does not matter with which materials are used to
make the copy.

\item[Targz's cap of life and wizardry.]
The
cap
is a
leather skull cap provides a bonus of two times the wearer's Hit Points.
When the cap is removed the bonus Hit Points are lost.
If the character would drop to less than one Hit Point by removing the cap,
then the character's Hit Points are reduced to one.
It also provides the wearer with a bonus being able to cast 1.5 times more spells
per day, or 1.5 times the wearer's P.P.E.
The wearer regenerates both at the twice the normal rate.

\item[Targz's wizardly robes.]
The wearer of this quilted and indestructible armour
gaines a bonus of +20\% elemental spell magic damage.
This item, if it exists, is the dream of warlocks everywhere.

\item[Zan's guardian.]
This is a small metal shield which is indestructible.
Furthermore, the shield magically absorbs the first ten
points of damage
suffered by the defender, or the armour he or she
is wearing.

\item[Zan's Vengeance.] This magical
but unassuming longsword
does 3D6 +3 damage and is also +3 to Parry and to Strike.
When used simultaneously with Zen's guardian,
anyone attacking the character does so with a -2
penalty.
\end{description}

\section{The alchemist's shop}
This section provides an overview of some specific items
that are commonly found in the inventories of alchemists
around the known world.
These items are magical but as magical items go they are
relatively commonplace.
Procuring them is usually not a problem,
but,
of course,
there is always a chance that an item will not be available
when the characters go looking for it.
These items may also be used as treasure and rewards for
completing adventures.

\subsection{Doubling guantlets}
When engaged in unarmed combat or fighting with a 
non-magical melee weapon,
the character's strike damage is replaced with the following
damage rolled a 1D6 when engaging supernatural evil but not mortal
foes in which case there is no changes to damage:
\begin{table}[h]
\centering
\begin{tabular}{rll}
\toprule
{\bfseries Roll} & \multicolumn{2}{c}{{\bfseries Damage}} \\ 
1&$=$&2 \\ 
2&$=$&4 \\ 
3&$=$&8 \\ 
4&$=$&16 \\ 
5&$=$&32 \\ 
6&$=$&64 \\
\bottomrule
\end{tabular}
\caption{Doubling damage.}
\label{table-doublingchaos}
\end{table}

\subsection{The transformer}
This magical device allows characters to construct their own
magical items.
The device can be constructed out of any suitable container
(one that is large enough to hold a sword, for instance).
The transformer is like a summoner's circle:
there are very specific recipes that yield very
specific results.
Some recipes may be discovered by trial and error
but this is very dangerous.

\section{The spell book}
There are many magical spells that have yet to be
discovered.
There are other invocations which
are known only to a
few mages across the megaverse.
The invocations listed here are some from those.

\subsection{Level Four}\label{sect:level-four-spells}
\subsubsection{Animate Object}
{\bfseries Range:} 40 feet (12 m) plus 10 feet (3 m)
per level of experience.\\
{\bfseries Duration:} Four
minutes per level of the Warlock.\\
{\bfseries Saving Throw:} None.\\
{\bfseries P.P.E.:} Twelve.

\noindent
This powerful element magic enables
the Warlock to animate any wood,
clay, or stone object weighing
less than 50 pounds (22 kg).

And this is the other paragraph that
gives us something about this spell
description and what not.

\noindent
{\textbf Limitations:}
\begin{itemize}
\item 200 pounds (90 kg) of raw material
per level of experience for the Earth Warlock,
with roughly 200 S.D.C.

The final product is high quality metal ready for
industrial use---construction, smelting, etc.
It cannot be used to magically repair
finished products such as power and body armour,
robots, vehicles, etc., except as raw materials
that are taken, retooled and used by
manufacturers.
\item Mega-Damage Steel can
be ``recycled'' provided that
M.D.C.\ metal scraps are avaiable.

{\bfseries Note:} This spell can not be used to turn perfectly
good metals/materials, machinery, vehicles,
or devices connected toa  power
source into a raw materials.
\end{itemize}
{\bfseries Mud Mound:}
\begin{description}
\item[M.D.C.:] 250
\item[Attributes:]
Made of mud, eith feet (2.4 m) toall,
I.Q. 8, M.A. 3, M.E. 10, Supernatural P.S. 25,
P.P. 19, speed 20, can ooze through
cracks.
\item[Notes:] The mound can carry up to 1250 pounds (563 kg) and still
moves at its maximum speed.
\end{description}

\section{Legendary magic users}\label{sec:legendary-mages}

\subsection{Fick}

\subsection{Talon}

\subsection{Targz}

